\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-21 paper/supplement.tex
finished drafts of all supplement captions, added supplement table

\renewcommand{\thefigure}{S\arabic{figure}}

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=1\textwidth]{figs/free_recall_behavior}
\caption{\textbf{Free recall behavioral results.  a--e. Immediate free
  recall.}  \textbf{a. Probability of first recall.}  Probability of
recalling each studied word first, as a function of its presentation
position.  \textbf{b. Lag Conditional Response Probability.}
Probability of recalling the word presented at position $i +
\mathrm{Lag}$ following the recall of the word presented at position
$i$.  \textbf{c. Clustering scores.}  Each score denotes participants'
tendancies to successively recall (cluster) words according to the
given feature dimension~\citep{PolyEtal09}: word length, starting letter, (semantic)
category, size (large or small), or presentation position (temporal).
\textbf{d. Serial position curve.}  Probability of recalling each word
as a function of its presentation position.  \textbf{e. Recall
  accuracy.}  Distribution of the average proportions of recalled
words, across all lists studied by each participant.  \textbf{f--j.
  Delayed free recall.}  These panels are in the same formats as
Panels a -- e, but they reflect performance on the delayed free recall
memory tests.  All panels: error bars and error ribbons denote bootstrap-estimated
95\% confidence intervals.  Shading (saturation) denotes results for
different subsets of participants, according to the average
proporition of words they remembered (group boundaries are indicated
by the colored lines in Panels e and j).}
\label{fig:fr_behavioral}
\end{sidewaysfigure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
\caption{\textbf{Spatial learning behavioral results.}
  \textbf{a--b. Estimation error.}  Estimation
  error is defined as the Euclidean distance between each shape's
  studied and recalled positions.  The bars show the average
  estimation error (across all shapes for each memory test) versus the
  number of memorized shapes.  \textbf{a. Slope.} Estimation errors
  are broken down by the slopes of regresion lines fit to each
  participant's estimation errors as a function of the number of
  memorized shapes.  Shallower slopes (i.e., smaller decreases in
  performance associated with memorizing more shapes) are reflected by
  more saturated coloring.  Error bars denote bootstrap-estimated 95\%
  confidence intervals.  \textbf{b. Intercept.}  Bars are in the same
  format as Panel a, but here estimation errors are
  broken down by the intercepts of the same regressions used in Panel
  a.  Smaller intercepts (i.e., smaller baseline errors) are reflected
  by more saturated coloring.  \textbf{c. Distribution of slopes.}
  Across-participant distribution of regression slopes.  The lines
  denote quartile boundaries (colors are matched to Panel a).  The
  slopes are multiplied by -1 and normalized to be within the [0, 1]
  interval such that (adjusted) slopes closer to 1 reflect better
  performance and slopes closer to 0 reflect worse performance.
  \textbf{b. Distribution of intercepts.}  Across-participant
  distribution of regression intercept terms.  The lines denote
  quartile boundaries (colors are matched to Panel b).  The intercepts
  are multiplied by -1 and normalized to be within the [0, 1] interval
  such that (adjusted) intercepts closer to 1 reflect better
  performance and intercepts closer to 0 reflect worse performance.}
\label{fig:spatial_behavioral}
\end{figure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_distributions}
\caption{\textbf{Distributions of fitness measures.}}
\label{fig:fitness_dists}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_dists_immediate}
\caption{\textbf{Distributions of fitness measures, broken down
    by immediate task performance.}}
\label{fig:fitness_dists_immediate}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
\caption{\textbf{Scatterplots of fitness measures versus
    immediate task performance measures.}}
\label{fig:fitness_scatters_immediate}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_dists_delayed}
\caption{\textbf{Distributions of fitness measures, broken down
    by delayed task performance.}}
\label{fig:fitness_dists_delayed}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
\caption{\textbf{Scatterplots of fitness measures versus
    delayed task performance measures.}}
\label{fig:fitness_scatters_delayed}
\end{sidewaysfigure}

\begin{figure}[p]
\centering
\includegraphics[width=0.4\textwidth]{figs/behavior_behavior_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    behavioral measures.}}
\label{fig:behavioral_corrs}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_fitness_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    fitness measures.}}
\label{fig:fitness_corrs}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/survey_survey_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    demographic measures.}}
\label{fig:survey_corrs}
\end{figure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/behavior_fitness+survey_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    behavioral measures and fitness or demographic measures.}}
\label{fig:fitness_survey_corrs}
\end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity}
\caption{\textbf{History of fitness activity levels weighted by
    behavioral performance.}}
\label{fig:activity_timecourse}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/weighted_timecourse_HR}
\caption{\textbf{History of cardiovascular activity weighted by
    behavioral performance.}}
\label{fig:HR_timecourse}
  \end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep}
\caption{\textbf{History of sleep efficiency and duration weighted by
    behavioral performance.}}
\label{fig:sleep_timecourse}
\end{figure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity_MH}
\caption{\textbf{History of fitness activity levels weighted by
    mental health factors.}}
\label{fig:activity_timecourse_MH}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=\textwidth]{figs/weighted_timecourse_HR_MH}
\caption{\textbf{History of cardiovascular activity weighted by
    mental health factors.}}
\label{fig:HR_timecourse_MH}
  \end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep_MH}
\caption{\textbf{History of sleep efficiency and duration weighted by
    mental health factors.}}
\label{fig:sleep_timecourse_MH}
  \end{figure}

>>>>

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=1\textwidth]{figs/free_recall_behavior}
\caption{\textbf{Free recall behavioral results.  a--e. Immediate free
  recall.}  \textbf{a. Probability of first recall.}  Probability of
recalling each studied word first, as a function of its presentation
position.  \textbf{b. Lag Conditional Response Probability.}
Probability of recalling the word presented at position $i +
\mathrm{Lag}$ following the recall of the word presented at position
$i$.  \textbf{c. Clustering scores.}  Each score denotes participants'
tendencies to successively recall (cluster) words according to the
given feature dimension~\citep{PolyEtal09}: word length, starting letter, (semantic)
category, size (large or small), or presentation position (temporal).
\textbf{d. Serial position curve.}  Probability of recalling each word
as a function of its presentation position.  \textbf{e. Recall
  accuracy.}  Distribution of the average proportions of recalled
words, across all lists studied by each participant.  \textbf{f--j.
  Delayed free recall.}  These panels are in the same formats as
Panels a -- e, but they reflect performance on the delayed free recall
memory tests.  All panels: error bars and error ribbons denote bootstrap-estimated
95\% confidence intervals.  Shading (saturation) denotes results for
different subsets of participants, according to the average
proportion of words they remembered (group boundaries are indicated
by the colored lines in Panels e and j).}
\label{fig:fr_behavioral}
\end{sidewaysfigure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
\caption{\textbf{Spatial learning behavioral results.}
  \textbf{a--b. Estimation error.}  Estimation
  error is defined as the Euclidean distance between each shape's
  studied and recalled positions.  The bars show the average
  estimation error (across all shapes for each memory test) versus the
  number of memorized shapes.  \textbf{a. Slope.} Estimation errors
  are broken down by the slopes of regression lines fit to each
  participant's estimation errors as a function of the number of
  memorized shapes.  Shallower slopes (i.e., smaller decreases in
  performance associated with memorizing more shapes) are reflected by
  more saturated coloring.  Error bars denote bootstrap-estimated 95\%
  confidence intervals.  \textbf{b. Intercept.}  Bars are in the same
  format as Panel a, but here estimation errors are
  broken down by the intercepts of the same regressions used in Panel
  a.  Smaller intercepts (i.e., smaller baseline errors) are reflected
  by more saturated coloring.  \textbf{c. Distribution of slopes.}
  Across-participant distribution of regression slopes.  The lines
  denote quartile boundaries (colors are matched to Panel a).  The
  slopes are multiplied by -1 and normalized to be within the [0, 1]
  interval such that (adjusted) slopes closer to 1 reflect better
  performance and slopes closer to 0 reflect worse performance.
  \textbf{b. Distribution of intercepts.}  Across-participant
  distribution of regression intercept terms.  The lines denote
  quartile boundaries (colors are matched to Panel b).  The intercepts
  are multiplied by -1 and normalized to be within the [0, 1] interval
  such that (adjusted) intercepts closer to 1 reflect better
  performance and intercepts closer to 0 reflect worse performance.}
\label{fig:spatial_behavioral}
\end{figure}

\clearpage
\begin{table}[]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{1.5in}p{4in}p{1.5in}}
\textbf{Abbreviation}   & \textbf{Description}
  & \textbf{Units}                           \\
  \hline
Resting HR              & Average daily resting heart rate                                                                                                                                                     & beats per minute (BPM)                   \\
  \hline
HR variability          & Heart rate variability (average daily variation between heartbeats)                                                                                                                  & milliseconds (ms)                        \\
  \hline
Steps                   & Number of steps taken each day                                                                                                                                                       & steps (count)                            \\
  \hline
Distance                & Estimated distance traveled each day                                                                                                                                                 & kilometers (km)                          \\
  \hline
Elevation               & Estimated daily elevation gain                                                                                                                                                       & feet (ft)                                \\
  \hline
Floors climbed          & Estimated number of daily floors climbed                                                                                                                                             & floors (count)                           \\
  \hline
Light activity          & Number of estimated daily minutes spent doing low-intensity activity                                                                                                                 & minutes (min)                            \\
  \hline
Fair activity           & Number of estimated daily minutes spent doing moderate-intensity activity                                                                                                            & minutes (min)                            \\
  \hline
High intensity activity & Number of estimated daily minutes spent doing high-intensity activity                                                                                                                & minutes (min)                            \\
  \hline
Excess calories         & Number of estimated daily calories burned minus estimated calorie intake                                                                                                             & calories (cal)                           \\
  \hline
Out-of-range HR         & Number of daily minutes spent with a heart rate lower than the "fat burn" heart rate zone (50\% of the maximum heart rate); maximum heart rate is defined as 220 minus age, in years & minutes (min)                            \\
  \hline
Fat burn HR             & Number of daily minutes spent with a heart rate between 50\% and 69\% of the maximum heart rate                                                                                      & minutes (min)                            \\
  \hline
Cardio HR               & Number of daily minutes spent with a heart rate between 70\% and 84\% of the maximum heart rate                                                                                      & minutes (min)                            \\
  \hline
Peak HR                 & Number of daily minutes spent with a heart rate between 85\% and 100\% of the maximum heart rate                                                                                     & minutes (min)                            \\
  \hline
Sleep duration          & Estimated number of hours slept during the prior 24 hour period                                                                                                                      & hours (hr)                               \\
  \hline
BMI                     & Body mass index, calculated as the
                          individual's weight (in kg) divided by their
                          height (in m) squared
  & kilograms per meter squared (kg/m\textsuperscript{2}) \\
  \hline
Body fat                & Estimated percentage of body fat (as a proportion of the individual's total weight)                                                                                                  & percentage (\%)                          \\
  \hline
Weight                  & Logged or measured weight                                                                                                                                                            & kilograms (kg)                           \\
  \hline
Water intake            & Self-reported water intake                                                                                                                                                           & 8 ounce cups (count)                     \\
  \hline
Coffee intake           & Self-reported coffee intake                                                                                                                                                          & 8 ounce cups (count)                    
\end{tabular}%
}
\caption{\textbf{Abbreviations of fitness-related measures.}  The
  abbreviations and descriptions provided in the table apply to the
  main text and supplement.}
\label{tab:abbreviations}
\end{table}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_distributions}
\caption{\textbf{Distributions of fitness measures.}  All
  abbreviations and measures are described in
  Table~\ref{tab:abbreviations}.  \textbf{a. Recent measures.}
  Daily values of each measure, averaged over the week prior to each
  participant's test day.  \textbf{b. Baselined measures.}  Daily
  values of each measure, averaged over the week prior to each
  participant's test day and divided by the average taken over the
  preceding 30 days.  \textbf{c. Static measures.} For each measure,
  only the most recently logged values are considered.  All panels:
  note that not all measures were captured for all participants.  Only
participants whose Fitbit records logged each given measure are
included in the distribution(s) for that measure.}
\label{fig:fitness_dists}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_dists_immediate}
\caption{\textbf{Distributions of fitness measures, broken down
    by immediate task performance.}  The distributions of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are broken down by
  participants' performance on each immediate recall test
  (Figs.~\immediateBehavior, \ref{fig:fr_behavioral},
  \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and \ref{fig:spatial_behavioral})}
\label{fig:fitness_dists_immediate}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
\caption{\textbf{Scatterplots of fitness measures versus
    immediate task performance measures.}  The scatterplots of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
  participants' performance on each immediate recall test
  (Figs.~\immediateBehavior, \ref{fig:fr_behavioral}, \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and \ref{fig:spatial_behavioral})}
\label{fig:fitness_scatters_immediate}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_dists_delayed}
\caption{\textbf{Distributions of fitness measures, broken down
    by delayed task performance.} The distributions of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are broken down by
  participants' performance on each delayed recall test
  (Figs.~\delayedBehavior, \ref{fig:fr_behavioral},
  \ref{fig:nat_behavioral}, and \ref{fig:vocab_behavioral})}
\label{fig:fitness_dists_delayed}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
\caption{\textbf{Scatterplots of fitness measures versus
    delayed task performance measures.} The scatterplots of recent
  (Panel a), baselined (Panel b), and static (Panel c) fitness
  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
  participants' performance on each delayed recall test
  (Figs.~\delayedBehavior, \ref{fig:fr_behavioral},
  \ref{fig:nat_behavioral}, and \ref{fig:vocab_behavioral})}
\label{fig:fitness_scatters_delayed}
\end{sidewaysfigure}

\begin{figure}[p]
\centering
\includegraphics[width=0.4\textwidth]{figs/behavior_behavior_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    behavioral measures.}  The measures are described and summarized in the
  distributions shown in Figures~\ref{fig:fr_behavioral},
  \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and
  \ref{fig:spatial_behavioral}.
The reported values denote the correlation coefficient between the
given row and column.  Only statistically reliable correlations are
displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
  analysis}, main text).}
\label{fig:behavioral_corrs}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_fitness_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    fitness measures.}  Fitness measures are described in summarized
  in Table~\ref{tab:abbreviations}.  The reported values denote the correlation coefficient between the
given row and column.  Only statistically reliable correlations are
displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
  analysis}, main text).}
\label{fig:fitness_corrs}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/survey_survey_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    demographic measures.}  Demographic measures are described in the
  main text (\textit{Participants}).  The reported values denote the correlation coefficient between the
given row and column.  Only statistically reliable correlations are
displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
  analysis}, main text).}
\label{fig:survey_corrs}
\end{figure}

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/behavior_fitness+survey_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    behavioral measures and fitness or demographic measures.}  All
  measures and abbreviations in this figure use the same notations as
  Figures~\ref{fig:behavioral_corrs}, \ref{fig:fitness_corrs}, and
  \ref{fig:survey_corrs}.  Only statistically reliable correlations are
displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
  analysis}, main text).}
\label{fig:fitness_survey_corrs}
\end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity}
\caption{\textbf{History of fitness activity levels weighted by
    behavioral performance.}  This figure is in the same format as
  Figure~\dynamics a and b, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:activity_timecourse}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/weighted_timecourse_HR}
\caption{\textbf{History of cardiovascular activity weighted by
    behavioral performance.}  This figure is in the same format as
  Figure~\dynamics a and b, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:HR_timecourse}
  \end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep}
\caption{\textbf{History of sleep efficiency and duration weighted by
    behavioral performance.}  This figure is in the same format as
  Figure~\dynamics a and b, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:sleep_timecourse}
\end{figure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity_MH}
\caption{\textbf{History of fitness activity levels weighted by
    mental health factors.}  This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:activity_timecourse_MH}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=\textwidth]{figs/weighted_timecourse_HR_MH}
\caption{\textbf{History of cardiovascular activity weighted by
    mental health factors.} This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:HR_timecourse_MH}
  \end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep_MH}
\caption{\textbf{History of sleep efficiency and duration weighted by
    mental health factors.} This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:sleep_timecourse_MH}
  \end{figure}
